\documentclass{beamer}

%\usepackage{beamerthemesplit}
%\usetheme{Madrid}
%\usepackage{pgf}
\usecolortheme{orchid}

%\hyphenpenalty=5000
%\tolerance=1000

\title{Decision Trees and Industrial Machine Learning}
\author{Jeremy Barnes, Recoset \\ (jeremy@recoset.com)}
\date{\today}

\begin{document}

\begin{frame}
  \titlepage
  \begin{center}
    www.recoset.com \\
  \end{center}
\end{frame}

\begin{frame}{Contents}
  \begin{itemize}
  \item Decision Trees
  \item Industrial Machine Learning
  \item My toolbox
  \end{itemize}
\end{frame}

\begin{frame}{About Me}
  
  \begin{itemize}
  \item Started using ML in 1999 at University
  \item Computational Linguistics (Idilia)
  \item ML Consulting
  \item E-commerce recommendations and online advertising (Recoset)
  \end{itemize}
  
  \item Mine your silo of historical data to optimize your future
\end{itemize}

Where we use Python?
\begin{itemize}
  \item Rapid prototyping of Mathematical Algorithms
  \item Analytical infrastructure (glue that holds algorithms together)
  \item Data munging
\end{itemize}

We're hiring well-rounded people who know how to deal with data!

\end{frame}

\begin{frame}{A Well-Rounded Company}

\begin{itemize}
  \item Startup: lots of jobs to do
  \item Use the most efficient tool for the job!
  \item Tools: Python, Javascript, C++, R, Ruby, Java, Clojure, ...
  \item Amplifiers: Mathematics, Statistics, Machine Learning
  \item We need Well-Rounded people
\end{itemize}

\end{frame}

\begin{frame}{The Well-Rounded Startup Employee}

\begin{centering}

\begin{tabular}{ll}
\textbf{Attribute}         &  \textbf{Value}  \vspace{0.5cm} \\

Creativity                 &  ideas        \\ 
Culture                    &  choices      \vspace{0.5cm} \\ 

Personality                &  teamwork     \vspace{0.5cm} \\

Programming/IT             &  tools        \\
Science                    &  amplifiers   \\
Engineering/Management     &  scaling      \vspace{0.5cm} \\ 

Experience                 &  risk, speed         
\end{tabular}

\end{centering}

\end{frame}

\begin{frame}{It's Worth Real Money}
\end{frame}

\begin{frame}{Stepping Back...}

Well-Rounded?
\begin{itemize}
  \item Knowledge
  \item Culture
  \item Creativity
  \item Personality
  \item Experience
\end{itemize}

\end{frame}

\begin{frame}{Bill Clinton}

\begin{itemize}
  \item Experience: (Former) Leader of the Free World? (check)
  \item Creativity: language manipulation (``I did not...'')? (check)
  \item Personality: Steamy romps with interns? (check)
  \item Knowledge: 
  \item \alert{Culture and Personality}: Plays the saxophone? (check)
\end{itemize}

Playing the saxophone makes Bill Clinton more cultured and personable, and came to define him as a person.

This makes him more well-rounded to people, which helped him to win elections.

\end{frame}

\begin{frame}

It's worth trying to be well-rounded.

You can get a lot of knowledge and culture with Python.

But don't stop there!

\vskip 1cm
\textit{We're hiring well-rounded people who know how to deal with data!}

\end{frame}



\end{document}
